---
title: "R Notebook"
output: html_notebook
---

### This is the analysis of the WM-MA-math ability manuscript

# version 1.0

## Table of contentes

1.  Load libraries

2.  Import, prepare data  & descriptives

  2.1 Data plots

3.  Estimate networks

  3.1 Network descriptives

  3.2 Network plot

4.  Network stability

4.1 Plot network stability

5.  SEM model

5.1 Model 1 WM as two systems

5.2 Model 2 WM as a single system

5.3 Models plots


## 1. Load libraries

````{r,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
  library("qgraph")
  library("dplyr")
  library("bootnet")
  library("mgm")
  library("lavaan")
  library("Hmisc")
  library("lavaanPlot")
  library("moments")
  library("readr")
  library("corrplot")
  library("semPlot")
```

## 2.  Import, prepare data  & descriptives

```{r, echo=FALSE, eval=TRUE, results='hold',,message=FALSE}
  setwd("/home/nachshon/Documents/NumericalHaifa/WM_MAProject")
  data <- read_csv("MEforR.csv")
  
  print("skewness")
  skewness(data)
  
  print("kurtosis")
  kurtosis(data)

  data1 <- data[-c(1)]
  print("Means and SDs")
  colMeans(data1, na.rm=T)
  as.vector(sapply(data1, sd, na.rm=T))
  print("correlation matrix")
  
  corr <- rcorr(as.matrix(data1))
  print(corr)
```
### 2.1 data plots
```{r, echo=FALSE}
hist(data)
corrplot(corr[["r"]], method = "number", type="lower")
```

## 3.  Estimate networks
```{r, echo=FALSE, eval=TRUE, results='hold',,message=FALSE}
 network1 <- estimateNetwork(data1, 
                              default="EBICglasso",
                              corMethod = "cor_auto",
                              tuning = 0.5)
  print("Partial correlation matrix")
  network1$graph
```

### 3.1 network descriptive

```{r,echo=FALSE, eval=TRUE,message=FALSE}
  fit1 <- mgm(data1, type=rep('g', 7), lev=rep(1,7)) 
  pred1 <- predict(fit1, data1, error.continuous='VarExpl')

```
```{r,echo=FALSE, eval=TRUE,message=FALSE,results='hold'}
print("Mean predictive value of variables: ") 
  mean(pred1$error$R2)
  print("Max predictor: ") 
  max(pred1$error$R2)
  print("Min predictor: ")
  min(pred1$error$R2)
```


### 3.2 Network plot

```{r,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
network1G <- plot(network1, layout = , theme="colorblind", pie=pred1$error$R2,
                    border.width=2, vsize=10, 
                  border.color='#555555', label.color="#555555", color="#EEEEEE")

  centralityPlot(network1, include =c("Strength","Closeness","Betweenness"))
```


## 4. Network stability 

```{r,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE,results='hide'}
  invisible(boot1a <- bootnet(network1, nBoots = 1000, nCores = 12))
  invisible(boot1b <- bootnet(network1, nBoots = 1000, type = "case",  nCores = 12))
  
  invisible(cs <- corStability(boot1b)) 
  
   
```
```{r, echo=FALSE, eval=TRUE, results='hold'}
print(cs)
```

### 4.1 Plot network stability
```{r, echo=FALSE}
  plot(boot1a)
  
  plot(boot1b, legend = FALSE)
  
```

## 5. Sem models
```{r, echo=FALSE}
 
  model1 <- '
  # measurement model
    WM =~ Nspan + Opposites
    MathAbility =~ Fluency + Calculation
  # regressions
    MathAbility ~ 1*WM + MARS + PSWQ + Colors
  # residual correlations
    WM ~~ MARS
    WM ~~ PSWQ
    MARS ~~ PSWQ
    Colors ~~ WM
    Colors ~~ PSWQ
    Colors ~~ MARS
  '
  model2 <- '
    # measurement model
    WM =~ Nspan + Colors + Opposites
    MathAbility =~ Fluency + Calculation
  # regressions
    MathAbility ~ WM + MARS + PSWQ
  # residual correlations
    WM ~~ MARS
    WM ~~ PSWQ
    MARS ~~ PSWQ
  '
```
### 5.1 Model 1 WM as two systems
```{r, echo=FALSE, eval=TRUE, results='hold'}
  fit1 <-  lavaan::sem(model1, data=data1, estimator="WLSM")
  summary(fit1, standardized=TRUE, fit.measures=T) 
  inspect(fit1,"r2")
```

### 5.2 Model 2 WM as a single system
```{r, echo=FALSE, eval=TRUE, results='hold'}
  fit2 <-  lavaan::sem(model2, data=data1, estimator="WLSM")
  summary(fit2, standardized=TRUE, fit.measures=T) 
  inspect(fit2,"r2")
```

### 5.3 Model plots


```{r, echo=FALSE}
lavaanPlot(model = fit1, 
             node_options = list(shape = "box", fontname = "Helvetica"), 
             edge_options = list(color = "grey"), coefs = TRUE, stand = TRUE, sig = 0.05)
  
lavaanPlot(model = fit2,
             node_options = list(shape = "box", fontname = "Helvetica"), 
             edge_options = list(color = "grey"), coefs = TRUE, stand = TRUE, sig = 0.05)
```